Using a Two-Layer Neural Network and Physicochemical Properties to Classify Glass for Forensic Analysis

### 2017-06-29 Paper/paper.tex
Code edits

\subsection{Training Algorithm}
\label{sec4.2}
%We chose to use the Scaled Conjugate Gradient (SCG) algorithm to train our network as it is very efficient for pattern recognition problems. For multi-layer networks, the Levenberg-Marquardt algorithm is often used, but it does not work well for pattern recognition as the transfer function in the output layer is operating outside the linear region. The scaled conjugate gradient algorithm is a special type of backpropagation. In backpropagation, we adjust the weights in the direction of steepest descent...

>>>>

\subsection{Training Algorithm}
\label{sec4.2}
We chose to use the Scaled Conjugate Gradient (SCG) algorithm to train our network as it is very efficient for pattern recognition problems. For multi-layer networks, the Levenberg-Marquardt algorithm is often used, but it does not work well for pattern recognition as the transfer function in the output layer is operating outside the linear region. The scaled conjugate gradient algorithm is a special type of backpropagation. In backpropagation, we adjust the weights in the direction of steepest descent...
